---
title: "distdecay"
output:
  rmarkdown::html_vignette:
    self_contained: no

  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r opts, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = TRUE,
  message = TRUE,
  width = 120,
  comment = "#>",
  fig.retina = 2,
  fig.path = "README-"
)
```


[![Build Status](https://travis-ci.org/mpadge/distdecay.svg?branch=master)](https://travis-ci.org/mpadge/distdecay) 
[![Build status](https://ci.appveyor.com/api/projects/status/github/mpadge/distdecay?svg=true)](https://ci.appveyor.com/project/mpadge/distdecay)
[![codecov](https://codecov.io/gh/mpadge/distdecay/branch/master/graph/badge.svg)](https://codecov.io/gh/mpadge/distdecay)
[![Project Status: WIP](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#WIP)


An R package for analysis of distance decay functions.

Input: Two square matrices; one of relationships between pairs of locations and
one of corresponding distances.

Output: Distance decay functions for each location, quantified as either
covariance or mutual information coefficients.

The package is primarily intended to analyse ``flow'' matrices which quantify
flows between locations, quantifed in such terms as rates or densities or
movement or exchange.

### Installation

```{r, eval=FALSE}
devtools::install_github("mpadge/distdecay")
```

